Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-02 main.tex
new title and two todos

    \title{Adaptive Scheduling of Scientific Workflows\\
%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
%should not be used}
    % \thanks{Identify applicable funding agency here. If none, delete this.}
    }

@@

    \subsubsection{Workflow instances}
    The input data for the experiments consists of two sets of workflows: real-world workflows
    obtained from~\cite{ewels2020nf} and workflows obtained by simulating real-world workflows
    with the WFGen generator~\cite{COLEMAN202216}.
    First, we discuss how the graph topology is generated,
    then we focus on the weights associated to tasks and edges.

@@

    \subsubsection{Target computing systems}
    To fully benefit from the historical data, the  {\em default} experimental environment
    that we consider is a cluster based on the same six
    kinds of real-world machines that were used in the experimental evaluation in~\cite{lotaru}.
    We set the number of each kind of node to six, thus having 36 processors in total. % the whole cluster.

@@

    \subsection{Results \skug{Full: 3, Polished: 2}}
    \subsubsection{Normal cluster}

>>>>

    \title{Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\
%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
%should not be used}
    % \thanks{Identify applicable funding agency here. If none, delete this.}
    }

@@

    \subsubsection{Workflow instances}
    \skug{Todo: describe the workflows the same asin the abstract}
    The input data for the experiments consists of two sets of workflows: real-world workflows
    obtained from~\cite{ewels2020nf} and workflows obtained by simulating real-world workflows
    with the WFGen generator~\cite{COLEMAN202216}.
    First, we discuss how the graph topology is generated,
    then we focus on the weights associated to tasks and edges.

@@

    \subsubsection{Target computing systems}
    \skug{Check that the description of speeds and memories is plausible and consistent with experimental setup. esp check for 19200 -> 192 GB.}
    To fully benefit from the historical data, the  {\em default} experimental environment
    that we consider is a cluster based on the same six
    kinds of real-world machines that were used in the experimental evaluation in~\cite{lotaru}.
    We set the number of each kind of node to six, thus having 36 processors in total. % the whole cluster.

@@

    \subsection{Results \skug{Full: 3, Polished: 2}}
    \subsubsection{Static experiments}
    \paragraph{Normal cluster}
